\documentclass{article}
\usepackage[T1]{fontenc}
\usepackage[total={6.5in, 9in}]{geometry}

%\usepackage{times}
%\usepackage{pslatex}
%\usepackage[utf8x]{inputenc}
%\usepackage{listings}
%\setlength{\textwidth}{6in}
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
%\setlength{\textheight}{8.85in}
%\setlength{\columnsep}{2.0pc}
%\setlength{\textwidth}{7in}
%\setlength{\topmargin}{0.15in}
%\setlength{\headsep}{0.0in}
%\setlength{\oddsidemargin}{-.19in}
\setlength{\parindent}{1pc}
\usepackage[linktocpage]{hyperref}
\usepackage{enumitem}
\setlist[itemize]{noitemsep}
\usepackage{etaremune}
\usepackage{libertine}
%\usepackage[compact]{titlesec}

% Set your name here
\def\name{\textrm{{Neil Shah}}}
%\rmfamily

\markright{\name}
\thispagestyle{empty}

\begin{document}

% Place name at left
{\Huge \bf \textsc{\name}}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}
\begin{tabular}[t]{cc}
 \begin{minipage}[t,left]{0.5\linewidth}
 Research Scientist \\
 \href{http://www.snap.com}{Snap Inc.} \\
 Santa Monica, CA
 \end{minipage} \hfill \quad \quad \quad \quad \quad \quad \quad \begin{minipage}[t,right]{0.5\linewidth}
  Email: \texttt{{\fontfamily{pcr}\selectfont nshah[at]snap[dot]com}}\\
  Last Update: \today
\end{minipage}
\end{tabular} \\

\section*{\bf \textsc{Education}}
\vspace{-5mm}\HRule
\begin{itemize}
\item \textbf{Ph.D}: Computer Science, Carnegie Mellon University, August 2013 - October 2017 \\
Advisor: \href{http://www.cs.cmu.edu/~christos}{Prof. Christos Faloutsos}.
\item \textbf{M.S}: Computer Science, Carnegie Mellon University, August 2013 - May 2017
\item \textbf{B.S}: Computer Science (Minor in Mathematics), North Carolina State University, August 2010 - May 2013 \\
  GPA: \textbf{4.0/4.0 - rank 1}, \emph{Summa Cum Laude} with \emph{Honors}
\end{itemize}

\section*{\bf \textsc{Positions}}
\vspace{-5mm}\HRule
\begin{itemize}
\item {\bf Snap Inc.}, Research Scientist. \\ My work spans computational user modeling and user understanding, especially in the contexts of misbehavior, abuse and fraud on web platforms. \\ December 2017 - present
\item {\bf Carnegie Mellon University}, Graduate Researcher. \\ I worked in the Computer Science Department, on algorithms and applications for anomaly detection in large social graphs. \\ August 2013 - October 2017
\item {\bf Twitch}, Visiting Researcher. \\  I worked on anti-abuse technologies as a member of the Science team.  \\ January 2016 - May 2016
\item {\bf Microsoft Research - Redmond}, Research Intern. \\  I worked on improving metrics and methods for measuring research impact for Microsoft Academic Search.  \\ June 2015 - August 2015
\item {\bf Lawrence Livermore National Laboratory}, Research Intern. \\  I worked on developing algorithms to automatically identify patterns and anomalies in time-evolving graphs. \\ June 2014 - August 2014
\item {\bf IBM - Silicon Valley}, Software Intern. \\ I worked in the IBM BigInsights group, with a focus on indexing and analytics of system log data.  \\ May 2012 - January 2013
\item {\bf North Carolina State University}, Undergraduate Researcher. \\ I worked in the Department of Computer Science on compressing and indexing large scientific datasets. \\ June 2009 - April 2013
\end{itemize}

\section*{\bf \textsc{Awards \& Distinctions}}
\vspace{-5mm}\HRule
\begin{itemize}
\item ACM SIGCHI Best Research Paper Honorable Mention Award, 2019
\item Symantec Graduate Research Fellowship Finalist, 2017
\item ACM SIGKDD Best Research Paper Award, 2016
\item National Science Foundation Graduate Research Fellowship, 2013
\item North Carolina State University College of Engineering Senior Award for Scholarly Achievement, 2013
\item North Carolina State University Department of Computer Science Senior Faculty Scholar, 2012
 \item National Science Foundation Research Experience for Undergraduates Grant, 2011
 \item North Carolina State University College of Engineering Dean's Research Assistantship, 2011
\item North Carolina State University Caldwell Fellowship, 2011
\item Coca-Cola Scholarship, 2010
\item Zinch Scholarship, 2010
\item National Merit Scholarship, 2010
\item CompTIA Information Technology Merit Award, 2010
\item 2nd place, National Siemens Competition in Math, Science and Technology, 2009
\item 1st place, Regional Siemens Competition in Math, Science and Technology, 2009
\end{itemize}

\section*{\bf \textsc{Publications}}
\vspace{-5mm}\HRule

\subsection*{\bf {Refereed Conference Publications}}
\begin{etaremune}[itemsep=1pt,parsep=0pt]

\item {\bf Neil Shah}. \emph{FARE: Schema-Agnostic Anomaly Detection in Social Event Logs}, DSAA 2019

\item Hamed Nilforoshan, {\bf Neil Shah}.  \emph{SliceNDice: Mining Suspicious Multi-attribute Entity Groups with Multi-view Graphs}, DSAA 2019.

\item Hemank Lamba, {\bf Neil Shah}.  \emph{Modeling Dwell Time Engagement on Visual Multimedia}, KDD 2019.  

\item Hana Habib, {\bf Neil Shah}, Rajan Vaish.  \emph{Impact of Contextual Factors on Public Snapchat Sharing}, CHI 2019. {\bf Best Paper Honorable Mention Award}.

\item Shreya Jain, Dipankar Niranjan, Hemank Lamba, {\bf Neil Shah}, Ponnurangam Kumaraguru.  \emph{Characterizing and Detecting Livestreaming Chatbots}, ASONAM 2019

\item Gisel Batista Guacho, Sara Abdali, {\bf Neil Shah}, Evangelos Papalexakis.  \emph{Semi-Supervised Content-based Detection of Misinformation via Tensor Embeddings}, ASONAM 2018.  

\item Nikhil Gupta, Dhivya Eswaran, {\bf Neil Shah}, Leman Akoglu, Christos Faloutsos. \emph{Beyond Outlier Detection: LookOut for Pictorial Explanation}, ECML-PKDD 2018.

\item Rohan Kumar, Mohit Kumar, {\bf Neil Shah}, Christos Faloutsos. \emph{Did We Get It Right? Predicting Query Performance in E-commerce Search}, SIGIR eCom 2018.

\item {\bf Neil Shah}, Hemank Lamba, Alex Beutel and Christos Faloutsos. \emph{The Many Faces of Link Fraud}, ICDM 2017.

\item Da-Cheng Juan, {\bf Neil Shah}, Mingyu Tang, Zhiliang Qian, Diana Marculescu, Christos Faloutsos. \emph{M3A: Model, MetaModel, and Anomaly Detection in Web Searches}, DSAA 2017.

\item {\bf Neil Shah}. \emph{FLOCK: Combating Astroturfing on Livestreaming Platforms}, WWW 2017.

\item {\bf Neil Shah}, Alex Beutel, Bryan Hooi, Leman Akoglu, Stephan Gunnemann, Disha Makhija, Mohit Kumar, Christos Faloutsos. \emph{EdgeCentric: Anomaly Detection in Edge-Attributed Networks}, ICDM DMCS 2016.

\item Bryan Hooi, Hyun Ah Song, Alex Beutel, {\bf Neil Shah}, Kijung Shin, Christos Faloutsos. \emph{FRAUDAR: Bounding Graph Fraud in the Face of Camouflage}, KDD 2016.  {\bf Best Paper Award}.

\item Yike Liu, Tara Safavi, {\bf Neil Shah}, Danai Koutra. \emph{Reducing Million-Node Graphs to a Few Structural Patterns: A Unified Approach}, KDD MLG 2016.

\item Yike Liu, {\bf Neil Shah}, Danai Koutra. \emph{An Empirical Comparison of the Sumarization Power of Graph Clustering Methods}, NIPS NSIS 2015.

\item Bryan Hooi, {\bf Neil Shah}, Alex Beutel, Stephan Gunnemann, Leman Akoglu, Mohit Kumar, Disha Makhija, Christos Faloutsos. \emph{BIRDNEST: Bayesian Inference for Ratings-Fraud Detection}, SDM 2016.

\item {\bf Neil Shah}, Danai Koutra, Tianmin Zou, Brian Gallagher, Christos Faloutsos. \emph{TimeCrunch: Interpretable Dynamic Graph Summarization}, KDD 2015.

\item Maria Giatsoglou, Despoina Chatzakou, {\bf Neil Shah}, Alex Beutel, Stephan Guenneman, Christos Faloutsos, Athena Vakali. \emph{ND-Sync: Detecting Synchronized Fraud Activities}, PAKDD 2015.

\item Maria Giatsoglou, Despoina Chatzakou, {\bf Neil Shah}, Christos Faloutsos, Athena Vakali. \emph{Retweeting Activity on Twitter: Signs of Fraud}, PAKDD 2015.

\item {\bf Neil Shah}, Alex Beutel, Brian Gallagher, Christos Faloutsos. \emph{Spotting Suspicious Link Behavior with fBox: An Adversarial Perspective}, ICDM 2014.

\item {\bf Neil Shah}, Eric Schendel, Saurabh Pendse, Sriram Lakshminarasimhan, Terry Rogers, Nagiza Samatova. \emph{Improving I/O Throughput with PRIMACY: Preconditioning ID-Mapper for Compressing Incompressibility}, CLUSTER 2012.

\item Eric Schendel, Ye Jin, {\bf Neil Shah}, Jackie Chen, Choong-Seock Chang, Seung-Hoe Ku, Stephane Ethier, Scott Klasky, Robert Latham, Robert Ross, Nagiza Samatova. \emph{ISOBAR Preconditioner for Effective and High-throughput Lossless Data Compression}, ICDE 2012.

\item Isha Arkatkar, John Jenkins, Sriram Lakshminarasimhan, {\bf Neil Shah}, Eric Schendel, Stephane Ethier, Choong-Seock Chang, Jackie Chen, Hemant Kolla, Scott Klasky, Robert Ross, Nagiza Samatova. \emph{Analytics-driven Lossless Data Compression for Rapid In-situ Indexing, Storing and Querying}, DEXA 2012.

\item Ye Jin, Sriram Lakshminarasimhan, {\bf Neil Shah}, Zhenhuan Gong, Choong-Seock Chang, Jackie Chen, Stephane Ethier, Hemant Kolla, Seung-Hoe Ku, Scott Klasky, Robert Latham, Robert Ross, Karen Schuchardt, Nagiza Samatova. \emph{S-preconditioner for Multi-fold Data Reduction with Guaranteed User-controlled Accuracy}, ICDM 2011.

\item Sriram Lakshminarasimhan, {\bf Neil Shah}, Stephane Ethier, Scott Klasky, Robert Latham, Robert Ross, Nagiza Samatova. \emph{Compressing the Incompressible with ISABELA: In-situ Reduction of Spatio-Temporal Data}, EuroPar 2011.

\item {\bf Neil Shah}, Yekaterina Shpanskaya, Choong-Seock Chang, Seung-Hoe Ku, Anatoli Melechko, Nagiza Samatova. \emph{Automatic and Statistically Robust Spatio-temporal Detection and Tracking of Fusion Plasma Fronts}, SciDAC 2010.

\item  Paul Breimyer, Guruprasad Kora, William Hendrix, {\bf Neil Shah}, Nagiza Samatova. \emph{pR: Automatic Parallelization of Data-parallel Statistical Computing Codes for R in Hybrid Multi-node and Multi-core Environments}, IADIS 2009.

\end{etaremune}


\subsection*{\bf {Refereed Journal Publications}}
\begin{etaremune}[itemsep=0pt,parsep=0pt]

\item Yike Liu, Tara Safavi, {\bf Neil Shah}, Danai Koutra. \emph{Reducing Large Graphs to Small Supergraphs: A Unified Approach}, Social Network Analysis and Mining 2018.

\item {\bf Neil Shah}, Danai Koutra, Lisa Jin, Tianmin Zou, Brian Gallagher, Christos Faloutsos. \emph{On Summarizing Large-Scale Dynamic Graphs}, Data Engineering Bulletin 2017.

\item Danai Koutra, {\bf Neil Shah}, Joshua T. Vogelstein, Brian Gallagher, Christos Faloutsos. \emph{DeltaCon: A Principled Massive-Graph Similarity Function with Attribution}, Transactions on Knowledge and Data Discovery 2015.

\item Sriram Lakshminarasimhan, {\bf Neil Shah}, Stephane Ethier, Scott Klasky, Robert Latham, Robert Ross, Nagiza Samatova. \emph{ISABELA for Effective In-situ Compression of Scientific Data}, Concurrency and Computation: Practice and Experience 2011.
	
\end{etaremune}

\subsection*{\bf {Book Chapters}}

\begin{etaremune}[itemsep=0pt,parsep=0pt]

\item Srijan Kumar, {\bf Neil Shah}.  \emph{False Information on the Web and Social Media: A Survey}, Social Media Analytics: Advances and Applications.

\item {\bf Neil Shah}. \emph{Introduction to R},
\href{http://www.crcpress.com/product/isbn/9781439860847}{Practical Graph Mining with R}.

\item Kanchana Padmanabhan, Sriram Lakshminarasimhan, Zhenhuan Gong, John Jenkins, {\bf Neil Shah}, Eric Schendel, Isha Arkatkar, Robert Ross, Scott Klasky, Nagiza Samatova. \emph{In-situ Analysis in Support of Exploratory Scientific Discovery in Data-Intensive Science},
\href{http://www.crcpress.com/product/isbn/9781439881392}{Data-Intensive Science}.

\end{etaremune}


\section*{\bf \textsc{Academic Experience}}
\vspace{-5mm}\HRule

\subsection*{\bf {Service and Mentoring}}

\begin{itemize}
  \item PC Chair for WSDM Cup (2020)    
  \item PC Chair for ASONAM Industrial Track (2019)
  \item PC Chair for WWW Cybersafety Workshop (2019)
  \item Invited Keynote Speaker for WWW Cybersafety Workshop (2018)
  \item Invited Keynote Speaker for KDD Outlier Detection De-constructed Workshop (2018)
  \item Invited Keynote Speaker for ECML-PKDD PhD Forum (2018)
  \item Session Chair for WWW ``Security and Privacy'' track (2018)
  \item Session Chair for ICDM ``Social'' track (2016)
  \item Program Committee for WSDM (2019)
  \item Program Committee for KDD (2019)
  \item Program Committee for WWW (2015, 2018)
  \item Program Committee for SDM (2018)
  \item Program Committee for CIKM (2017)
  \item Program Committee for ICDM Demo Session (2019)
   \item Program Committee for WSDM ``Misinformation and Misbehavior Mining on the Web'' Workshop (2018)
    \item Program Committee for  ICDM Demo Session (2018)
   \item Program Committee for KDD ``Mining and Learning with Graphs'' Workshop (2017, 2018, 2019)
 \item Program Committee for WSDM ``Heterogeneous Networks Analysis and Mining'' Workshop (2017, 2018)
 \item Program Committee for  ICDM PhD Forum (2017)
 \item Reviewer for ACM ``Transactions on Knowledge Discovery from Data' Journal (2018, 2019, 2020)
 \item Reviewer for Springer ``Data Mining and Knowledge Discovery'' Journal (2018, 2019)
 \item Reviewer for ACM ``Transactions on Social Computing'' Journal (2018, 2019)
 \item Reviewer for ACM ``Transactions on Knowledge and Data Engineering'' Journal (2016, 2017)
 \item Reviewer for CSCW (2019)
 \item Reviewer for CHI (2019)
 \item Reviewer for WISE (2014)
 \item Reviewer for IPDPS (2011)
  \item Mentored Parisa Kaghzagaran (intern at Snap Research)
 \item Mentored Dipankar Niranjan (BS student at IIIT Delhi)
 \item Mentored Shreya Jain (BS student at IIIT Delhi)
 \item Mentored Mr. Himel Dev (intern at Snap Research)
 \item Mentored Mr. Hamed Nilforoshan (intern at Snap Research)
 \item Mentored Mrs. Hana Habib (intern at Snap Research)
 \item Mentored Mr. Rohan Kumar (visiting CS student at CMU)
 \item Mentored Mr. Hemank Lamba (ISR PhD student at CMU)
 \item Mentored Ms. Qicheng Huang (EE PhD student at CMU)
 \item Mentored Ms. Chenlei Fang (EE PhD student at CMU)
 \item Mentored Mr. Tianmin Zou (CS MS student at CMU)
\end{itemize}

\subsection*{\bf {Funding}}
\begin{itemize}
\item Contributed towards Flipkart faculty grant (with CMU: Bryan Hooi, Dhivya Eswaran, Christos Faloutsos)
\item Contributed towards Wharton Customer Analytics Initiative proposal ``Fraud Detection through Mining Dynamic Behavior for Group Anomalies'' (with CMU: Alex Beutel and Christos Faloutsos)
\item Contributed towards PNC Center for Financial Services proposal PF15003: ``Fraud Detection in Financial Data'' (with CMU: Alex Beutel and Christos Faloutsos)
\item Contributed towards proposal DOE-NNSA-30788.1.1990222 ``Quantifying Network Changes'' (with CMU: Danai Koutra and Christos Faloutsos)
\item Contributed towards proposal NSF IIS-1028746 ``Collaborative Research:  Understanding Climate Change: A Data Driven Approach'' (with NCSU: Nagiza Samatova and Fredrick Semazzi)
\end{itemize}

\subsection*{\bf {Teaching}}
\begin{itemize}
\item Guest Lecture ``A Foray into Graph Mining'' for USC CSCI-699 Introduction to Information Extraction, by Prof. \href{http://ink-ron.usc.edu/xiangren/}{Xiang Ren}
\item Guest Lecture ``Graph Mining for Fraud Detection'' for CMU 15-300 Research and Innovation in Computer Science, by Prof. \href{http://www.cs.cmu.edu/~tcm}{Todd Mowry}
\item Teaching Assistant for CMU 15-300 Research and Innovation in Computer Science, by Prof. \href{http://www.cs.cmu.edu/~tcm}{Todd Mowry}
\item Teaching Assistant for CMU 15-826 Multimedia Databases and Data Mining, by Prof. \href{http://www.cs.cmu.edu/~christos}{Christos Faloutsos}
\end{itemize}

\section*{\bf \textsc{Technical Skills}}
\vspace{-5mm}\HRule
\begin{itemize}
\item Cloud Platforms: GCP, AWS
\item Programming Languages/Tools: Python, Java, C, C++, x86 Assembly
\item Web Languages/Tools: SQL, HTML, PHP, JavaScript, CSS, WordPress
\item Engineering Tools: Matlab, R
\item Typesetting Tools: \LaTeX, Microsoft Office, LibreOffice
\item Source Code Management Tools: Git, Subversion
\item Operating Systems: Microsoft Windows, Ubuntu Linux, Mac OSX
\end{itemize}

\section*{\bf \textsc{Graduate Coursework}}
\vspace{-5mm}\HRule
\subsection*{\bf {Carnegie Mellon University}}

\begin{itemize}
\item \emph{Advanced and Distributed Operating Systems} with Prof. \href{http://www.cs.cmu.edu/~dga}{Dave Andersen},

\item \emph{Multimedia Databases and Data Mining} with Prof. \href{http://www.cs.cmu.edu/~christos}{Christos Faloutsos}

\emph{Graduate Algorithms} with Prof. \href{http://www.cs.cmu.edu/~mblum}{Manuel Blum}

\item \emph{Machine Learning} with Profs. \href{http://www.cs.cmu.edu/~epxing}{Eric Xing} and \href{http://www.cs.cmu.edu/~aarti}{Aarti Singh}

\item \emph{Randomized Algorithms} with Prof. \href{http://www.cs.cmu.edu/~haeupler}{Bernhard Haeupler}

\item \emph{Programming Language Semantics} with Prof. \href{http://www.cs.cmu.edu/~aplatzer}{Andr{\'e} Platzer}
\end{itemize}


\subsection*{\bf {North Carolina State University}}

\begin{itemize}
\item \emph{Automated Learning \& Data Analysis} with Prof. \href{http://www.csc.ncsu.edu/people/nfsamato}{Nagiza Samatova}, 
 
\item \emph{Software Engineering} with Prof. \href{http://web.engr.illinois.edu/~taoxie}{Tao Xie}, 

\item \emph{Database Management Concepts \& Systems} with Prof. \href{http://www.csc.ncsu.edu/people/tyu}{Ting Yu}
\end{itemize}

%\section*{\bf \textsc{Research Interests}}
%\HRule
%%\paragraph{}
%\begin{itemize}
% \item Anomaly and fraud detection on large social and information networks
% \item User behavior on social networks
% \item Applications of data mining and network analysis
%\end{itemize}

\section*{\bf \textsc{References}}
\vspace{-5mm}\HRule
\vspace{1em}
Available upon request.

\bigskip


\end{document}

